Pleiades: Interactive Composing Tools for Vega-Lite Charts

### 2019-06-12 final/paper/paper.tex
typo

%% indicate IEEE Member or Student Member in form indicated below
\author{Chanwut Kittivorawong, Manesh Jhawar, Sorawee Porncharoenwase}
\authorfooter{
%% insert punctuation at end of each item
\item
 Chanwut Kittivorawong is an undergraduate Computer Science student at the University of Washington. E-mail: chanwutk@cs.washington.edu.
\item
 Manesh Jhawar is an undergraduate Computer Science student at the University of Washington. E-mail: mj06@uw.edu.
\item
 Sorawee Porncharoenwase is a graduate Computer Science student at the University of Washington. E-mail: sorawee@cs.washington.edu.
}

@@

As we expected, the results show that Pleiades gives users a better understanding
and ease them at composing different charts and see what fits the best.
The key idea behind why Pleiades makes composing charts
easier and more intuitive is because the process allows users to compose small
charts and rearrange them into a bigger charts. We call this approach
\emph{bottom-up}. This contrasts with Vega-lite's \emph{top-down approach}
which demands users to know the layout of the entire structure already
beforehand and hence is very rigid and inflexible. Also, the graphical user interface
provided used with a smoother way to compose charts, than to write nested JSON specs.

One interesting result we found was that the ability to perform
the four operations gave users a better understanding of these operations
and how to properly use then. The validation steps, along with the error message
that Pleiades provides helps users to understand what they are doing wrong,
helping them in their education about visualization in general.

@@

%% if specified like this the section will be committed in review mode
\acknowledgments{
The authors wish to thank A, B, C. This work was supported in part by
a grant from XYZ.}

>>>>

%% indicate IEEE Member or Student Member in form indicated below
\author{Chanwut Kittivorawong, Manesh Jhawar, Sorawee Porncharoenwase}
\authorfooter{
%% insert punctuation at end of each item
\item
 Chanwut Kittivorawong is an undergraduate Computer Science student at the University of Washington. E-mail: chanwutk@cs.washington.edu.
\item
 Manesh Jhawar is an undergraduate Computer Science student at the University of Washington. E-mail: mj06@cs.washington.edu.
\item
 Sorawee Porncharoenwase is a graduate Computer Science student at the University of Washington. E-mail: sorawee@cs.washington.edu.
}

@@

As we expected, the results show that Pleiades gives users a better understanding
and ease them at composing different charts and see what fits the best.
The key idea behind why Pleiades makes composing charts
easier and more intuitive is because the process allows users to compose small
charts and rearrange them into a bigger chart. We call this approach
\emph{bottom-up}. This contrasts with Vega-lite's \emph{top-down approach}
which demands users to know the layout of the entire structure already
beforehand and hence is very rigid and inflexible. Also, the graphical user interface
provided users with a smoother way to compose charts, than to write nested JSON specs.

One interesting result we found was that the ability to perform
the four operations gave users a better understanding of these operations
and how to properly use them. The validation steps, along with the error message
that Pleiades provides helps users to understand what they are doing wrong,
helping them in their education about visualization in general.

@@

%% if specified like this the section will be committed in review mode
% \acknowledgments{
% The authors wish to thank A, B, C. This work was supported in part by
% a grant from XYZ.}
